Order reduction and partial MILP models \\ for certifying Robustness of DNNs globally.

### 2025-07-28 AAAI2026/Lipitschz.tex
update tables

	\begin{subnumcases}{\forall b \in \ell, \Delta(\hat{b}) =}
		r(b)\Delta(b), & for $W_{bz} > 0$ \\
		\max(\Delta(b),-\sol(b)), & for $W_{bz} < 0$ and $\sol(b)\geq0$\\
		\max(0,\Delta(b)+\sol(b)), & for $W_{bz} < 0$ and $\sol(b)<0$ \quad \, \quad \, \quad		 
	\end{subnumcases}

@@

	\begin{proposition}
		$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
	\end{proposition}

@@

	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
	\begin{align*}
		& \begin{aligned}
			y_i + x'_i &\leq a\beta_i        &\quad\quad
			y_i + x'_i &\geq (1-a)\alpha_i \\
			x'_i       &\leq a'\beta_i       & 
			x'_i       &\geq (1-a')\alpha_i \\
			\hat{y}_i  &\leq a\gamma_i       &
			\hat{y}_i  &\geq -a'\gamma_i \\
			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
			\hat{y}_i  &\leq -x'_i + a\beta_i &
			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
		\end{aligned}
	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.

@@

	\begin{tabular}{|l|l|l|l|l|}\hline
		$L_{1,diff}\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
		1v,open 100 &     0.035613 &  0.035613 &                       0.01288 & 10608 \\\hline
		3v,open 100 &     0.040074 &  0.028934 &                      0.021441 & 10922 \\\hline
		3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
		2v,open 100 &     0.046719 &  0.024364 &                      0.024436 & 10922 \\\hline
	\end{tabular}

@@

	\begin{tabular}{|l|l|l|l|l|}\hline
		$L_{1,diff}\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
		1v,open 100 &     0.035613 &  0.035613 &                      0.019141 &   984 \\\hline
		3v,open 100 &     0.041382 &  0.025433 &                      0.016638 &  1082 \\\hline
		3v,open 100 &      0.03496 &  0.027206 &                      0.021607 & 14523 \\\hline
		3v,open 100 &     0.032906 &  0.027655 &                      0.016481 & 72126 \\\hline
		2v,open 100 &     0.041787 &  0.022805 &                      0.022882 &  1082 \\\hline
		2v,open 100 &     0.035964 &  0.023563 &                      0.023608 & 14523 \\\hline
	\end{tabular}

@@

	\begin{tabular}{|l|l|l|l|l|l|}\hline
		& Method & Bound & Solution & Real & Time \\\hline
		54 & 2v,open 75x5 & 21.013510 & 8.467282 & 0.222900 & 43200 \\\hline
		55 & 2v,open 90x5 & 12.009719 & 3.440846 & 0.258480 & 43200 \\\hline
		56 & 2v,open 97x5 & 20.646000 & 1.915210 & 0.372200 & 129626 \\\hline
		57 & 2v,open 100x5 & 8.760835 & nan & nan & 43200 \\\hline
		58 & 2v,open 100x5 & 8.257397 & nan & nan & 259200 \\\hline
		59 & 1v,open 75x5 & 17.472430 & 0.908984 & 0.091740 & 43200 \\\hline
	\end{tabular}

>>>>

		\begin{subnumcases}{\forall b \in \ell, \Delta(\hat{b}) =}
			r(b)\Delta(b),&for $W_{bz} > 0$ \\
			\max(\Delta(b),-\sol(b)),&for $W_{bz} < 0$ and $\sol(b)\geq0$\\
			\max(0,\Delta(b)+\sol(b)),&for $W_{bz} < 0$ and $\sol(b)<0$ \quad \, \quad \, \quad		 
		\end{subnumcases}

@@

	\begin{proposition}
		$0 \leq \Improve\max^z(a) \leq \Utility\max^z(a)$. 
	\end{proposition}

@@

	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
	\begin{align*}
		& \begin{aligned}
			y_i + x'_i &\leq a\beta_i        &
			y_i &+ x'_i \geq (1-a)\alpha_i \\
			x'_i       &\leq a'\beta_i       & 
			x'_i       &\geq (1-a')\alpha_i \\
			\hat{y}_i  &\leq a\gamma_i       &
			\hat{y}_i  &\geq -a'\gamma_i \\
			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
			\hat{y}_i  &\leq -x'_i + a\beta_i &
			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
		\end{aligned}
	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.

@@

	\vspace*{1ex}

	\begin{tabular}{|l|l|l|l|l|}\hline
		$\|d\|_1\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
		1v,open 100 &     0.035613 &  0.035613 &                       0.01288 & 10608 \\\hline
		3v,open 100 &     0.040074 &  0.028934 &                      0.021441 & 10922 \\\hline
		3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
		2v,open 100 &     0.046719 &  0.024364 &                      0.024436 & 10922 \\\hline
	\end{tabular}

		\vspace*{1ex}

@@

		\vspace*{1ex}

	\begin{tabular}{|l|l|l|l|l|}\hline
		$\|d\|_1\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
		1v,open 100 &     0.035613 &  0.035613 &                      0.019141 &   984 \\\hline
		3v,open 100 &     0.041382 &  0.025433 &                      0.016638 &  1082 \\\hline
		3v,open 100 &      0.03496 &  0.027206 &                      0.021607 & 14523 \\\hline
		3v,open 100 &     0.032906 &  0.027655 &                      0.016481 & 72126 \\\hline
		2v,open 100 &     0.041787 &  0.022805 &                      0.022882 &  1082 \\\hline
		2v,open 100 &     0.035964 &  0.023563 &                      0.023608 & 14523 \\\hline
	\end{tabular}

@@

	\begin{tabular}{|l|l|l|l|l|}\hline
		 Method & Bound & Solution & Real & Time \\\hline
		 2v,open 75x5 & 21.0135 & 8.4672& 0.2229 & 43200 \\\hline
		2v,open 90x5 & 12.0097 & 3.4408 & 0.2584 & 43200 \\\hline
	 2v,open 97x5 & 20.6460 & 1.9152 & 0.3722 & 129626 \\\hline
	 2v,open 100x5 & 8.7608 & nan & nan & 43200 \\\hline
		 2v,open 100x5 & 8.2573 & nan & nan & 259200 \\\hline
		 1v,open 75x5 & 17.4724 & 0.9089 & 0.0917 & 43200 \\\hline
	\end{tabular}
